### 2024-07-25 Scripts/Manuscript/manuscript.Rmd
rewriting based on feedback

abstract: |
  Recent studies have shown that challenges in measurement practices in original and replication research may have contributed to the “replication crisis” in psychological science. 
  However, the exact nature and extent of the association between measurement and replicability is not yet clear. 
  We investigated the reliability and measurement reporting of 77 measures within 56 Many Labs replications [@klein2014investigating; @ebersole2016many; @klein2018many; @ebersole2020many] and related original psychological studies, and whether these were associated with replicability.
  Results from logistic regression models indicated that questionable practices in measurement reporting in replication studies (b = -5.60, OR = 0.004, 95% [0,0.156]), but not the reliability of the measurement (b = 8.21, OR = 3677.542, 95% [1.271,1727601729.241]), was associated with lower replicability of the findings tested with that measure. <!-- the code for these two results is: ???; these lines will only work after code chunks 1, 2, 12, & 19 have been ran. -->
  Furthermore, not all measures in the original and replication studies were sufficiently reliable across contexts. 
  Additionally, we found that evidence on reliability and validity was rarely reported. 
  These findings corroborate existing research that shows that validity evidence is rarely reported, and that these reporting practices may have negative consequences for the informativeness of replications. 
  We offer suggestions on improving measurement validation and reporting practices. 
  Finally, we argue that researchers should evaluate the reported measurement information when deciding what studies to replicate.

@@

```{r setup, include = FALSE}
# loading R libraries
library(papaja)
library(worcs)
library(tidyr)
library(betareg)
library(lmerTest)
library(psych)
library(forcats)
library(GPArotation)
library(ggplot2)
library(ggridges)
library(GGally)
library(ggforce)
library(grid)
library(gridExtra)
library(metafor)

@@

But replications often fail. In 2015, the Replication Project: Psychology [RPP; @osc2015estimating] attempted replications of 100 research findings in psychology, they observed a substantial discrepancy between the replication findings and the original findings . Similarly, the Many Labs projects aimed to replicate the effects reported in original articles across different labs in various locations around the world [@klein2014investigating; @ebersole2016many; @klein2018many; @klein2022many; @ebersole2020many], and often found smaller effects in replications compared to original research. Furthermore, the estimates of the effect varied between different lab locations.

@@

The first issue relates to the concept of reliability, which gives an indication of how consistent the responses on a measurement are. Reliability is a critical first step to obtaining credible findings. Because if the scores on a measure are not consistent with themselves, it is unlikely that any effect associated with the measure can credibly be established. Psychometrics offers various ways to assess reliability empirically [e.g. @nunnally1978overview; @mellenbergh2011conceptual].

@@

Despite the importance of having reliable and valid measures, research has shown that Questionable Measurement Practices (QMPs) are not uncommon. QMPs are practices that raise doubts about a measurement's validity [@flake2020measurement], and have been coined as a term analogous to Questionable Research Practices [QRPs, @john2012measuring]. QMPs range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of a measure and procedure of an existing measure [@flake2020measurement]. More specifically,  @flake2020measurement identified six key questions than an article should answer to avoid QMPs: the definition of the construct, how the measure was selected, how the measure was operationalized, how the measure was quantified, whether it was modified or not and why, and the reasons and details of creating a measure if applicable. If these questions can be answered based on the reported measurement information, then reporting is sufficiently transparent to promote a more cumulative psychological science.

@@

Measurement reliability varies across samples. It is crucial for evaluating replications that differences between replication and original are understood and accounted for.

-   RQ1a. What is the reliability in replications of psychological research?
-   RQ1b. What is the reliability in original psychological research?

The Many Labs studies were intended as direct replications. In direct replications, any remaining deviations from the original research should be irrelevant for testing the same effect as the original study [@nosek2022replicability]. This means that, the reliability of measurements in replications should also not deviate systematically from the original research.

-   H1. No difference is present in the reliability between replication research and original psychological research.

Reliability has the potential to vary not only between replication and original research, but also across replicating labs assessing the same effect [@vacha-haase1998ReliabilityGeneralizationExploring].

-   RQ2. Do reliability estimates differ between replicating labs?

Heterogeneity in reliability may be contributing strongly to the variation in reliability between labs. However, for effect sizes there is little empirical evidence of widespread heterogeneity among the Many Labs replications [@klein2018many; @olsson2020heterogeneity]. We expect the same for the heterogeneity in reliability coefficients.

-   H2. There is no significant variation in the reliability estimates of replications of the same original study.

To see if reliability is related to replication success, we investigated whether successfully replicated studies differ in the reliability of their measures as compared to non-replicated studies.

-   RQ3. What is the association between replication study reliability and replication outcome?

Greater reliability means the variance around the estimate of the true effect is decreased [@nunnally1994assessment]. Assuming that the true effect is not null, then the statistical conclusions tested with reliable measures are more likely to converge to significance.

-   H3. Reliability in replication research is positively associated with successful replication of an original finding.

This study aims to conceptually replicate the findings on measurement reporting of @flake2022construct.

-   RQ4a. How common are QMPs in replications of psychological research?
-   RQ4b. How common are QMPs in original psychological research?

@flake2022construct found that QMPs were overall more common in the RPP replications as compared to the original research. We did not hypothesize this to be the case in the Many Labs sample, because of the use of structured protocols documenting the measurement.

-   H4. QMPs are more frequent in original psychological research than in replication research.

QMPs obscure information relevant to mimic measurement from original research in subsequent replication attempts. The resulting deviations in measurement may be partly responsible for deviations in replication and original effects [@flake2022construct].

-   RQ5. What is the association between QMPs in replication studies and replication outcome?

A reduction in QMPs corresponds to greater transparency in reporting of measurement. In line with earlier research finding other transparency related practices to be associated with more robust estimates of effects [@wicherts2011willingness; @protzko2020high], we expect:

-   H5. QMPs in replications are negatively associated with replication success.

QMPs obscure information about a particular measurement. This in turn may cause issues for reconstructing that measurement in subsequent replication attempts.

-   RQ6. What is the association between QMPs in original research and QMPs in replications of psychological research?

@flake2022construct already proposed that QMPs in original articles may cause issues for recreating measurements for replication research. @shaw2020measurement already found such a spill-over effect for validity. In line with this research we expect:

-   H6. The total number of QMPs in original psychological research is positively related to the total number of QMPs in replication research.

@@

This manuscript was created in RStudio [@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCS2021] to ensure reproducibility and transparency. All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> and <https://osf.io/9r8yt/>.

@@

The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each set of replications replicating a single original study across multiple labs. These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [Data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document.

@@

Cronbach's Alpha was calculated as the main reliability index used in the analyses, as it remains the most commonly used indicator of the reliability of a measure [@flake2017construct], thus allowing for comparisons with the reliabilities reported in original articles. Cronbach's Alpha was calculated using the alpha function from the psych R package [*v`r getNamespaceVersion("psych")[[1]]`*; @R-psych] with default arguments. Omega was pre-registered as an additional index of reliability, because it is regarded by numerous psychometricians as a more informative alternative to Cronbach’s Alpha [@crutzen2017scale; @deng2017testing]. The results based on Omega can be found in [Appendix C](../../SupplementaryMaterials/AppendixScripts/Appendix_multilevel_analyses.Rmd).

@@

After the initial coding, we made minor revisions to `r length(coded_data_revised_raw[1, c("Op1", "Op2", "Op5", "Sel1", "Sel3", "Quant1", "Quant2", "Quant3", "Mod1", "Mod2", "Mod3", "Mod4", "Mod5", "Mod6")])` of the `r length(coded_data_initial_raw[1, c("Def1", "Op1", "Op2", "Op3", "Op4", "Op5", "Sel1", "Sel2", "Sel3", "Sel4", "Quant1", "Quant2", "Quant3", "Quant4", "Mod1", "Mod2", "Mod3", "Mod4", "Mod5", "Mod6")])` QMP items in the preregistered coding protocol, because they were considered too stringent in some of their criteria for what constituted a QMP. For example, in the initial protocol an example item had to be present within the article or protocol itself, or else this was counted as a QMP. In the revised protocol, references to online appendices with example items were also considered sufficient for this item. The analyses, tables and figures presented in this article are all based on the revised coding protocol, the results of the equivalent analyses based on QMPs obtained with our initial protocol can be found in [Appendix D](../../SupplementaryMaterials/AppendixScripts/Appendix_initial_QMP_analyses.Rmd).

@@

Table \@ref(tab:ReplicationRatioTable) shows the number of replication sets, measures, and measures per study that were extracted, as well as the proportion of successful replications, for each of the Many Labs separately and in total.

```{r ReplicationRatioTable, warning = FALSE}
# construct the replication ratio table to be printed
replication_ratio_table <- data.frame("Many Labs Version" = c("1", "2", "3", "5", "Total"),
                                      "N Total" = c(table(coded_data_replications$many_labs_version), nrow(coded_data_replications)), 
                                      "N Replicated" = c(table(coded_data_replications$many_labs_version, coded_data_replications$hypothesis_support)[, "Yes"], table(coded_data_replications$hypothesis_support)["Yes"]))

# calculate the replication ratio from the N measures whose studies were replicated
# and the N total measures, per Many Labs study.
replication_ratio_table$"Replication Ratio" <- round(replication_ratio_table$N.Replicated / replication_ratio_table$N.Total, digits = 2)

# Changing column names to be less computer speak-y looking
colnames(replication_ratio_table) <- c("Many Labs Version", "Nr. Measures$^a$", 
                                       "Nr. Replicated", "Replication Ratio")

# adding a superscript for a later footnote
replication_ratio_table$"Nr. Replicated"[3] <- "$3^a$"

# print the table in apa formatting
apa_table(
  replication_ratio_table, align = c("l", "r", "r", "r")
  , caption = "Ratio of measures for which the effect was considered replicated, across many labs projects"
  , note = "Nr. measures refers to the total number of primary measures extracted, while Nr. replicated displays the number of measures for which the associated effect was replicated successfully. $^a$replication was assessed as unclear for three other measures, since their effect was only partially replicated. These have been treated as not replicated within this table and in further analyses throughout the article. "
  , escape = FALSE, placement = "htp", midrules = 4)

@@

@@

@@

The RG meta-analysis was performed using the *rma* function from the *metafor* R package [*v`r getNamespaceVersion("metafor")[[1]]`*; @R-metafor]. Defaults settings were used. We implemented no correction for bias, because the Many Labs replications were not at risk of publication bias.

@@

To get an indication of the true variability in the reliability scores, we used the RG meta-analyses to test for heterogeneity in the reliabilities in the replications. This analysis deviated from the multilevel analysis we preregistered, as the preregistered analysis was later deemed not suitable for testing Hypothesis 2 (results from the preregistered analysis are shown in [Appendix A](../../SupplementaryMaterials/AppendixScripts/Appendix_pre-reg_analyses.Rmd)).

@@

```{r Hypothesis3MainTest, include = FALSE}
## The main model to test hypothesis 3, through a logistic regression model.
H3_test_result_main_alpha <- apa_print(glm(formula = replication ~ 1 + alpha, 
                                      family = binomial(), data = data_h3_avg))

@@

# well this OR is quite a ridiculous number..., but then again a step from 0 alpha to 1 is quite a jump too...
H3_test_result_main_alpha$full_result$alpha

@@

Cronbach's alpha did not significantly predict replication success in the main logistic regression model (`r H3_main_full_results_alpha_with_OR`). Results based on the Omega coefficient lead to a similar conclusion (see [Appendix C](../../SupplementaryMaterials/AppendixScripts/Appendix_omega_analyses.Rmd)). However, it should be noted that the reliability coefficient could be calculated for only `r nrow(data_h3_avg)` measures. As a result, the estimates of the relation between reliability and replication success obtained using these models each come with large uncertainty.

@@

Reliability was more commonly reported in original (n = `r N_reported_reliabilities_original`) as compared to replication research (n = `r N_reported_reliabilities_replications_number_style`), $\chi^{2}$(`r apa_num(reliability_reporting_test_result$parameter)`) = `r apa_num(reliability_reporting_test_result$statistic)`, *p* = `r apa_p(reliability_reporting_test_result$p.value)`. Validity evidence was similarly reported infrequently. `r apa_num(sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` original articles reported validity evidence from a factor analysis, while only `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` replications did.

@@

We used a beta-regression model to test the difference in QMP ratio between original and replication was significant using the *betareg* R package [*v`r getNamespaceVersion("betareg")[[1]]`*; @R-betareg_a; @R-betareg_b]. Beta regression models are similar to other generalized linear regression models, but they are better suited to model dependent variables with values in the interval of $(0, 1)$, including ratios. Furthermore, they are robust for heteroskedastic and asymmetrically distributed dependent variables [@cribari2010beta].

```{r Hypothesis4Model, include = FALSE}
## Hypothesis 4 beta regression model
# running the models with revised QMP ratio's
H4_test_results_REV <- betareg(QMP_REV_ratio ~ rep_org, data = data_h4)
```

@@

We used logistic regression to test the association between the QMP ratio in replication protocols and replication success. In line with Hypothesis 5, results showed that successful replications were associated with fewer QMPs compared to unsuccessful replications (`r H5_test_results_REV_with_OR`). However, we did not find the association when based on the initial protocol (`r H5_test_results_with_OR`).

@@

>>>>

abstract: |
  Recent studies have shown that challenges in measurement practices may have contributed to the “replication crisis” in psychological science. 
  However, the nature and extent of the association between measurement and replicability remains unclear. 
  We investigated the reliability and measurement reporting of 77 measures within 56 Many Labs replications and related original articles [@klein2014investigating; @ebersole2016many; @klein2018many; @ebersole2020many], and their association with replicability. 
  Results from logistic regressions indicated that questionable practices in reporting on measurement (QMPs) in replication studies (b = -5.60, p = .006), but not its reliability (b = 8.21, p =. 106) was associated with lower replicability. <!-- the code to retrieve these two results is: paste0("$b = ", H3_test_result_main_alpha$table$estimate[[2]], "$, p = ", H3_test_result_main_alpha$table$p.value[[2]], "$") & paste0("$b = ", H5_test_results_REV$table$estimate[[2]], "$, p = ", H5_test_results_REV$table$p.value[[2]], "$"); these lines will only work after code chunks 1, 2, 12, & 19 have been ran.--> 
  Furthermore, Reliability Generalization Meta-analysis revealed that not all measures were sufficiently reliable across contexts. 
  We additionally found that reliability and validity evidence was rarely reported. 
  These findings corroborate existing research that construct validity in published research is low and that may have negative consequences for replications. 
  We offer suggestions on improving measurement practices, and argue that reported measurement information should inform the decision to replicate.

@@

```{r setup, include = FALSE}
# loading R libraries
library(papaja)
library(worcs)
library(tidyr)
library(betareg)
library(lmerTest)
library(psych)
library(forcats)
library(GPArotation)
library(ggplot2)
library(ggridges)
library(GGally)
library(ggforce)
library(grid)
library(gridExtra)
library(metafor)
library(sandwich)
library(lmtest)

@@

But replications often fail. In 2015, the Replication Project: Psychology [RPP\; @osc2015estimating] attempted replications of 100 research findings in psychology, they observed a substantial discrepancy between the replication findings and the original findings . Similarly, the Many Labs projects aimed to replicate the effects reported in original articles across different labs in various locations around the world [@klein2014investigating; @ebersole2016many; @klein2018many; @klein2022many; @ebersole2020many], and often found smaller effects in replications compared to original research. Furthermore, the estimates of the effect varied between different lab locations.

@@

The first issue relates to the concept of reliability, which gives an indication of how consistent the responses on a measurement are. Reliability is a critical first step to obtaining credible findings. Because if the scores on a measure are not consistent with themselves, it is unlikely that any effect associated with the measure can credibly be established. Psychometrics offers various ways to assess reliability empirically [@nunnally1978overview; @mellenbergh2011conceptual].

@@

Despite the importance of having reliable and valid measures, research has shown that Questionable Measurement Practices (QMPs) are not uncommon. QMPs are practices that raise doubts about a measurement's validity [@flake2020measurement], and have been coined as a term analogous to Questionable Research Practices [QRPs\; @john2012measuring]. QMPs range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of a measure and procedure of an existing measure [@flake2020measurement]. More specifically,  @flake2020measurement identified six key questions than an article should answer to avoid QMPs: the definition of the construct, how the measure was selected, how the measure was operationalized, how the measure was quantified, whether it was modified or not and why, and the reasons and details of creating a measure if applicable. If these questions can be answered based on the reported measurement information, then reporting is sufficiently transparent to promote a more cumulative psychological science.

@@

Measurement reliability varies across samples. Therefore, we investigated what the reliability is in replications of psychological research (RQ1a) and original psychological research (RQ1b).

The Many Labs studies were intended as direct replications. In direct replications, any remaining deviations from the original research should be irrelevant for testing the same effect as the original study [@nosek2022replicability]. As a result, we expected that there would be, no difference present in the reliability between replication research and original psychological research (H1).

Reliability has the potential to vary not only between replication and original research, but also across labs assessing the same effect [@vacha-haase1998ReliabilityGeneralizationExploring]. We thus investigated whether reliability estimates differed between replicating labs (RQ2).

Heterogeneity in reliability may be contributing strongly to the variation in reliability between labs. However, for effect sizes there is little empirical evidence of widespread heterogeneity among the Many Labs replications [@klein2018many; @olsson2020heterogeneity]. We expected that there would be no significant variation in the reliability estimates of replications of the same original study (H2) as well.

To see if reliability is related to replication success, we investigated whether there is an association between successfully replicated study reliability and replication outcome (RQ3).

Greater reliability means the variance around the estimate of the true effect is decreased [@nunnally1994assessment]. Assuming that the true effect is not null, then the statistical conclusions tested with reliable measures are more likely to converge to significance. THus, we expected to observe a positive association between reliability in replication research and successful replication of an original finding (H3).

### Measurement Reporting
This study aims to conceptually replicate the findings on measurement reporting of @flake2022construct. To do so we evaluate how common QMPs are in replications of psychological research (RQ4a) and original psychological research (RQ4b).

@flake2022construct found that QMPs were overall more common in the RPP replications as compared to the original research. We hypothesized that for our Many Labs sample QMPs would be more frequent in original psychological research than in replication research (H4), because of the use of structured protocols documenting the measurement.

QMPs obscure information relevant to mimic measurement from original research in subsequent replication attempts. The resulting deviations in measurement may be partly responsible for deviations in replication and original effects [@flake2022construct]. Thus we investigated whether QMPs in replication protocols were associated with the replication outcome (RQ5).

A reduction in QMPs corresponds to greater transparency in reporting of measurement. In line with earlier research finding other transparency related practices to be associated with more robust estimates of effects [@wicherts2011willingness; @protzko2020high], we expected QMPs in replications to be negatively associated with replication success (H5).

QMPs obscure information about a particular measurement. This in turn may cause issues for reconstructing that measurement in subsequent replication attempts. We investigated the association between QMPs in original research and QMPs in replications of psychological research (RQ6).

@flake2022construct already proposed that QMPs in original articles may cause issues for recreating measurements for replication research. @shaw2020measurement already found such a spill-over effect for validity. In line with this research we expected the total number of QMPs in original psychological research to be positively related to the total number of QMPs in replication research (H6).

@@

This manuscript was created in RStudio [@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [*v`r getNamespaceVersion("worcs")[[1]]`*\; @vanlissaWORCS2021] to ensure reproducibility and transparency. All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> and <https://osf.io/9r8yt/>.

@@

The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each set of replications replicating a single original study across multiple labs. These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [Data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document).

@@

Cronbach's Alpha was calculated as the main reliability index used in the analyses, as it remains the most commonly used indicator of the reliability of a measure [@flake2017construct], thus allowing for comparisons with the reliabilities reported in original articles. Cronbach's Alpha was calculated using the alpha function from the *psych* R package [*v`r getNamespaceVersion("psych")[[1]]`*\; @R-psych] with default arguments. Omega was pre-registered as an additional index of reliability, because it is regarded by numerous psychometricians as a more informative alternative to Cronbach’s Alpha [@crutzen2017scale; @deng2017testing]. The results based on Omega can be found in [Supplementary Analyses C](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_multilevel_analyses.Rmd).

@@

After the initial coding, we made minor revisions to `r length(coded_data_revised_raw[1, c("Op1", "Op2", "Op5", "Sel1", "Sel3", "Quant1", "Quant2", "Quant3", "Mod1", "Mod2", "Mod3", "Mod4", "Mod5", "Mod6")])` of the `r length(coded_data_initial_raw[1, c("Def1", "Op1", "Op2", "Op3", "Op4", "Op5", "Sel1", "Sel2", "Sel3", "Sel4", "Quant1", "Quant2", "Quant3", "Quant4", "Mod1", "Mod2", "Mod3", "Mod4", "Mod5", "Mod6")])` QMP items in the preregistered coding protocol, because they were considered too stringent in some of their criteria for what constituted a QMP. For example, in the initial protocol an example item had to be present within the article or protocol itself, or else this was counted as a QMP. In the revised protocol, references to online appendices with example items were also considered sufficient for this item. The analyses, tables and figures presented in this article are all based on the revised coding protocol, the results of the equivalent analyses based on QMPs obtained with our initial protocol can be found in [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd).

@@

Table \@ref(tab:ReplicationNrTable) shows the number of replication sets, measures, and measures per study that were extracted, as well as the proportion of successful replications, for each of the Many Labs separately and in total.

```{r ReplicationNrTable, warning = FALSE}
# construct the replication ratio table to be printed
replication_nr_table <- data.frame("Many Labs Version" = c("1", "2", "3", "5", "Total"),
                                      "N Total" = c(table(coded_data_replications$many_labs_version), nrow(coded_data_replications)), 
                                      "N Replicated" = c(table(coded_data_replications$many_labs_version, coded_data_replications$hypothesis_support)[, "Yes"], table(coded_data_replications$hypothesis_support)["Yes"]))

# Changing column names to be less computer speak-y looking
colnames(replication_nr_table) <- c("Many Labs Version", "Nr. Measures", 
                                       "Nr. Replicated")

# adding a superscript for a later footnote
replication_nr_table$"Nr. Replicated"[3] <- "$3^a$"

# print the table in apa formatting
apa_table(
  replication_nr_table, align = c("l", "r", "r")
  , caption = "Ratio of measures for which the effect was considered replicated, across many labs projects"
  , note = "Nr. measures refers to the total number of primary measures extracted, while Nr. replicated displays the number of measures for which the associated effect was replicated successfully. $^a$replication was assessed as unclear for three other measures, since their effect was only partially replicated. These have been treated as not replicated within this table and in further analyses throughout the article. "
  , escape = FALSE, placement = "htp", midrules = 4)

@@

```{r InformationOnMeasurementModification}
# Here we determine whether items had the number of items changed, and how.

# The code below indexes the scales for which either the number of items or 
# number of response options were decreased.

item_number_change_data <- coded_data_replications[!is.na(coded_data_replications$mod_5_REV) & coded_data_replications$mod_5_REV, c(1, 2, 3, 56)]

# Extracted information on the modification of measurement items. When NA is 
# reported it means that we found no modification of number of items.
item_number_change_data$context <- c("from 3 questions about 15 topics -> 1 question about four topics", NA, "from a list of quotations to only the 1 of interest", "From four IATs to 1 IAT in replications", "Initial study used 6 items from an 8-item short scale, 25-item four factor scale suggested by original authors, but 5-item subscale of specific factor of interest", NA,  "Original research had 19 scenarios, replication participants got randomly assigned to 1 control and 3 moral dilemmas from the set of 19", " from a 10-item scale, to single-item scale.", NA, NA, "Compared to the 'longer lists of anagrams used' in previous research (226 for 4 dimensions) on the topic, they switched to a shorter 4 anagram task of the 1 dimension of interest.", "Original measure assessed 4 constructs with 24 item, For the replication they switched to a different scale measuring the 1 construct relevant to the effect using 7 items.")

# Whether the change was a decrease or increase in items
item_number_change_data$direction <- as.factor(c("decrease", NA, "decrease", "decrease", "decrease", NA, "decrease", "decrease", NA, NA, "decrease", "increase"))

# sum(item_number_change_data$direction == "decrease", na.rm = TRUE)

# creating indexes for decreasing items to see if there are noteworthy differences.
decreased_items_index <- rep(FALSE, nrow(coded_data_replications))

# setting to true in case items were decreased.
decreased_items_index[as.numeric(rownames(item_number_change_data[item_number_change_data$direction == "decrease" & !is.na(item_number_change_data$direction),]))] <- TRUE

# getting information on hypothesis support
hypothesis_support_index <- coded_data_replications$hypothesis_support

hypothesis_support_index[coded_data_replications$hypothesis_support == "Unclear"] <- "Yes"

# coding Unclear into No instead of Yes didn't make a difference on the test.
# hypothesis_support_index[coded_data_replications$hypothesis_support == "Unclear"] <- "No"

# chi-squared test of differences in hypothesis support between measures for 
# which items were decreased and for which it was not.
chisq.test(decreased_items_index, coded_data_replications$hypothesis_support)

# Interestingly, when item numbers were decreased, the replicability seemed to have increased in this scenario.
# Although the difference was not significant and there were too few modifications to the items to get a stable estimate.

#mean(coded_data_replications$hypothesis_support[!as.numeric(rownames(coded_data_replications)) %in% as.numeric(rownames(item_number_change_data[item_number_change_data$direction == "decrease" & !is.na(item_number_change_data$direction),]))] == "Yes")

### Looking at the relevancy for Hypothesis tests.
# H1
coded_data_original_shortened$reliability_type[decreased_items_index]
coded_data_replications$reliability_type[decreased_items_index]

# Only one of these measures had a reported reliability in the original, so it
# is unlikely to have been of much impact.

# H2
coded_data_original_shortened$reliability_coeff[decreased_items_index]
coded_data_replications$reliability_coeff[decreased_items_index]

data_h3_avg[data_h3_avg$reporting_index %in% as.numeric(rownames(item_number_change_data[item_number_change_data$direction == "decrease" & !is.na(item_number_change_data$direction),])),]

# Of the measures we could calculate the reliability of, only the measure of 
# persistence was decreased in item count. This was interestingly the one with
# the lowest calculated average alpha in the sample.

@@

Because of this multilevel structure we initially planned to conduct multilevel models alongside our single-level regression models for testing Hypothesis 3, 5, and 6. However, these analyses were omitted, because group sizes were small. The results from these analyses are reported in [Supplementary Analyses B](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_multilevel_analyses.Rmd)) for the sake of completeness and transparency.

@@

The RG meta-analysis was performed using the *rma* function from the *metafor* R package [*v`r getNamespaceVersion("metafor")[[1]]`*\; @R-metafor]. Defaults settings were used. We implemented no correction for bias, because the Many Labs replications were not at risk of publication bias.

@@

To get an indication of the true variability in the reliability scores, we used the RG meta-analyses to test for heterogeneity in the reliabilities in the replications. This analysis deviated from the multilevel analysis we preregistered, as the preregistered analysis was later deemed not suitable for testing Hypothesis 2 (results from the preregistered analysis are shown in [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd)).

@@

```{r Hypothesis3MainTest, include = FALSE}
## The main model to test hypothesis 3, through a logistic regression model.
H3_test_main_alpha <- glm(formula = replication ~ 1 + alpha, 
                                 family = binomial(), data = data_h3_avg)

H3_test_result_main_alpha <- apa_print(H3_test_main_alpha)

@@

# well this OR is quite a ridiculous number..., but then again a step from 0 alpha to 1 is quite a jump too...
```

Cronbach's alpha did not significantly predict replication success in the main logistic regression model (`r H3_main_full_results_alpha_with_OR`). Results based on the Omega coefficient lead to a similar conclusion (see [Supplementary Analyses C](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_omega_analyses.Rmd)).

```{r Hypothesis3WhiteAdjustedSensitivityAnalysis, warning = FALSE}
# We take the H3_test_main_alpha result from the main analysis on the aggregate
# level as reported in the main text, and then calculate the White heteroskedastic 
# variance/covariance matrix for the coefficients
White_varcov_matrix <- vcovHC(H3_test_main_alpha, type = "HC1") # HC1 applies White's correction

# now we apply this covariance matrix to get robust standard errors on our estimation
H3_test_alpha_White_adjusted <- coeftest(H3_test_main_alpha, White_varcov_matrix)

H3_coefficient_alpha_White_adjusted <- H3_test_alpha_White_adjusted[2,1]

# first we calculate the odds-ratio
OR_coefficient_alpha_White_adjusted <- round(exp(H3_coefficient_alpha_White_adjusted), 2)

# then we also calculate the log-odds ratio CIs
log_OR_CI_LOW <- H3_coefficient_alpha_White_adjusted - (1.96 * H3_test_alpha_White_adjusted[2,2])
log_OR_CI_HI <- H3_coefficient_alpha_White_adjusted + (1.96 * H3_test_alpha_White_adjusted[2,2])

# and then convert them to odds ratio CIs
OR_CI_LOW <- round(exp(log_OR_CI_LOW), 2)
OR_CI_HI <- round(exp(log_OR_CI_HI), 2)

# now we create the string to print in text
H3_test_result_alpha_White_adjusted <- paste0("$\\hat{\\beta} = ", round(H3_test_alpha_White_adjusted[2,1], 2), "$, $OR = ", OR_coefficient_alpha_White_adjusted, "$, 95\\% CI $[", OR_CI_LOW, ", ", OR_CI_HI, "]$, $z = ", round(H3_test_alpha_White_adjusted[2,3], 2), "$, $p = ", apa_p(H3_test_alpha_White_adjusted[2,4]), "$")

@@

We additionally pre-registered a random intercept and random-slope multilevel regression model of the same relationship with each lab's unique reliability nested within the set of replication of an effect. However, because our dependent variable (replicability) is at the group level, we decided based on suggestions in the literature [@foster-johnson2018Predicting] to use a test on the aggregate level using White's heteroscedasticity adjustment to address the dependency. This analysis also showed a non-significant relation (`r H3_test_result_alpha_White_adjusted`). However, it should be noted that for these analyses the reliability coefficient could be calculated for only `r nrow(data_h3_avg)` measures. As a result, the estimates of the relation between reliability and replication success obtained using these models each come with large uncertainty.

@@

Reliability was more commonly reported in original (n = `r N_reported_reliabilities_original`) as compared to replication research (n = `r N_reported_reliabilities_replications_number_style`), $\chi^{2}$(`r apa_num(reliability_reporting_test_result$parameter)`) = `r apa_num(reliability_reporting_test_result$statistic)`, *p* = `r apa_p(reliability_reporting_test_result$p.value)`. Validity evidence was similarly reported infrequently. `r apa_num(sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` original articles reported validity evidence from a factor analysis, while only `r apa_num(sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` replications did. Furthermore, we conducted pre-registered exploratory analyses testing the unidimensionality of `r nrow(cfa_results)` measures with available replication data using a confirmatory factor analysis. We found that `r sum(cfa_results$Single_factor == "Yes")` of these measures met our criteria for unidimensionality (see [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd) for further details).

@@

We used a beta-regression model to test the difference in QMP ratio between original and replication was significant using the *betareg* R package [*v`r getNamespaceVersion("betareg")[[1]]`*\; @R-betareg_a; @R-betareg_b]. Beta regression models are similar to other generalized linear regression models, but they are better suited to model dependent variables with values in the interval of $(0, 1)$, including ratios. Furthermore, they are robust for heteroskedastic and asymmetrically distributed dependent variables [@cribari2010beta].

```{r Hypothesis4Model, include = FALSE}
## Hypothesis 4 beta regression model
# running the models with revised QMP ratio's
H4_test_results_REV <- betareg(QMP_REV_ratio ~ rep_org, data = data_h4)

@@

```{r Hypotheses5ReportedMultilevelAnalyses, include = FALSE, warning = FALSE}
## Hypothesis 5 sensitivity test using a random intercept Gaussian model.
# create dummy H5 dataframe for use in sensitivity test
data_h5_sens <- data_h5

# convert outcome variable to be usable with Gaussian distribution via
# logit transform.
data_h5_sens$QMP <- log(data_h5_sens$QMP_ratio /(1 - data_h5_sens$QMP_ratio))

# running the model with initial QMP ratio's
random_intercept_h5<- apa_print(lmer(formula = QMP ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens))
```

We used logistic regression to test the association between the QMP ratio in replication protocols and replication success. In line with Hypothesis 5, results showed that successful replications were associated with fewer QMPs compared to unsuccessful replications (`r H5_test_results_REV_with_OR`). However, we did not find the association with the initial protocol in neither the single-level (`r H5_test_results_with_OR`) nor the multilevel model (`r random_intercept_h5$full_result$QMP`)[^2].

[^2]: As of writing this article the *betareg* package does not allow for estimation of multilevel models. As an approximation, Gaussian random-intercept multilevel models were implemented using the *lmer* function from the *lme4* package [@R-lme4]. The outcome QMP ratio variable was transformed using the logit link function (the default link function in the *betareg* package) to fit the Gaussian model.

@@

# Using a glm to check if results differs in direction and significance from the 
# beta-regression, to check that including a linear regression line in figure 46
# is representative of the relationship.
H6_glm_test_REV <- glm(Rep_QMP_REV_ratio ~ QMP_REV_ratio, data = data_h6)

H6_glm_test_results_REV <- apa_print(H6_glm_test_REV)$full_result$QMP_REV_ratio
